---
title: "ParkingStat - South Lake Union (2018)"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, eval = T)
# Pre-load packages ----
library(tidyverse)
```

# Read parking data about South Lake Union in 2018.

```{r load_data}
df <- read_csv("data/2018_ParkingStat_SouthLakeUnion_Group.csv", show_col_types = F)
df$SourceElementKey <- as.character(df$SourceElementKey)
df$Month <- factor(month.abb[df$Month], level = month.abb)
.level_weekday <- c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat")
df$Weekday <- factor(.level_weekday[df$Weekday], level = .level_weekday)
```

# Exploratory data analysis
 
## Source element key in 8401, 8402.

| SourceElementKey | Blockface Name                                   | Side of Street |
|------------------|--------------------------------------------------|----------------|
| 8401             | 8TH AVE N BETWEEN REPUBLICAN ST AND MERCER SR ST | W              |
| 8402             | 8TH AVE N BETWEEN REPUBLICAN ST AND MERCER SR ST | E              |


### Facet data by Month

```{r facet-by-month-8401-8402}
df %>%
  filter(SourceElementKey %in% c(8401, 8402)) %>%
  ggplot(aes(
    x = Hour,
    y = ParkingRatio,
    color = SourceElementKey
  )) +
  geom_jitter(alpha = 0.5) +
  geom_smooth() +
  facet_wrap(~Month) +
  theme_bw() +
  theme(legend.position="bottom")
```

### Facet data by Weekday

```{r facet-by-weekday-8401-8402}
df %>%
  filter(SourceElementKey %in% c(8401, 8402)) %>%
  ggplot(aes(
    x = Hour,
    y = ParkingRatio,
    color = SourceElementKey
  )) +
  geom_jitter(alpha = 0.5) +
  geom_smooth() +
  facet_wrap(~Weekday) +
  theme_bw() +
  theme(legend.position="bottom")
```

### Facet data by Month and Weekday

```{r facet-by-month-and-weekday-8401-8402}
df %>%
  filter(SourceElementKey %in% c(8401, 8402)) %>%
  ggplot(aes(
    x = Hour,
    y = ParkingRatio,
    color = SourceElementKey
  )) +
  geom_jitter(alpha = 0.5) +
  geom_smooth() +
  facet_grid(Weekday ~ Month) +
  theme_bw() +
  theme(legend.position="bottom")
```

## Source element key started number 1.

### Facet data by Month

```{r facet-by-month-started-1}
df %>%
  filter(str_detect(SourceElementKey, "^1")) %>%
  ggplot(aes(
    x = Hour,
    y = ParkingRatio,
    color = SourceElementKey
  )) +
  geom_jitter(alpha = 0.5) +
  geom_smooth() +
  facet_wrap(~Month) +
  theme_bw() +
  theme(legend.position = "none")
```

### Facet data by Weekday

```{r facet-by-weekday-started-1}
df %>%
  filter(str_detect(SourceElementKey, "^1")) %>%
  ggplot(aes(
    x = Hour,
    y = ParkingRatio,
    color = SourceElementKey
  )) +
  geom_jitter(alpha = 0.5) +
  geom_smooth() +
  facet_wrap(~Weekday) +
  theme_bw() +
  theme(legend.position = "none")
```
